Gelation as condensation frustrated by hydrodynamics and mechanical tension

### 2016-10-01 manuscript4.tex
Comment out "effective volume fraction" according to mail exchanges between 17/11/2015 and 24/11/2015. Final word was "The percolation problem may be related to a large scale organization of structures helped by flow. This may lead to the failure of a simple argument based on effective volume, assuming the isotropic nature of structuring."

\documentclass[preprint,footinbib,amsmath,amssymb]{revtex4}
\usepackage{graphicx,amsmath}
\usepackage{color}
\begin{document}
\draft

\title{Gelation as condensation frustrated by hydrodynamics and mechanical tension}
\author{Hideyo Tsurusawa}
%\thanks{These authors contributed equally to this work}
\author{Mathieu Leocmach}
%\thanks{These authors contributed equally to this work}
\author{Hajime Tanaka}
%\email{tanaka@iis.u-tokyo.ac.jp}
\affiliation{ {Institute of Industrial Science, University of Tokyo, 4-6-1 Komaba, Meguro-ku, Tokyo 153-8505, Japan} }

@@

Consequently, long-lived elongated clusters have a higher probability to meet via either rotational or translational diffusion than compact spherical clusters. In Supplementary Figure~\ref{fig:effectiveVF} we show that indeed at all colloidal volume fraction percolation takes place when the effective volume fraction $\phi_\text{eff} = \sum\frac{4\pi}{3}R_g^3$ of the clusters reaches random close packing. Hydrodynamics explains why in a rather dilute regime we can observe immediate formation of elongated clusters and then their slow, hydrodynamically-assisted aggregation into a percolated structure.
We stress that this is a direct consequence of large-size disparity, which leads to the physical situation where discrete solid objects are floating in a continuum liquid.

>>>>

\documentclass[preprint,footinbib,amsmath,amssymb,superscriptaddress]{revtex4}
\usepackage{graphicx,amsmath}
\usepackage{color}
\begin{document}
\draft

\title{Gelation as condensation frustrated by hydrodynamics and mechanical tension}
\author{Hideyo Tsurusawa}
\affiliation{ {Institute of Industrial Science, University of Tokyo, 4-6-1 Komaba, Meguro-ku, Tokyo 153-8505, Japan} }
%\thanks{These authors contributed equally to this work}
\author{Mathieu Leocmach}
\affiliation{Univ Lyon, Université Claude Bernard Lyon 1, CNRS, Institut Lumière Matière, F-69622, VILLEURBANNE, France}
%\thanks{These authors contributed equally to this work}
\author{Hajime Tanaka}
%\email{tanaka@iis.u-tokyo.ac.jp}
\affiliation{ {Institute of Industrial Science, University of Tokyo, 4-6-1 Komaba, Meguro-ku, Tokyo 153-8505, Japan} }

@@

Consequently, long-lived elongated clusters have a higher probability to meet via either rotational or translational diffusion than compact spherical clusters. 
%In Supplementary Figure~\ref{fig:effectiveVF} we show that indeed at all colloidal volume fraction percolation takes place when the effective volume fraction $\phi_\text{eff} = \sum\frac{4\pi}{3}R_g^3$ of the clusters reaches random close packing. 
Hydrodynamics explains why in a rather dilute regime we can observe immediate formation of elongated clusters and then their slow, hydrodynamically-assisted aggregation into a percolated structure.
We stress that this is a direct consequence of large-size disparity, which leads to the physical situation where discrete solid objects are floating in a continuum liquid.
